% $Id$

% Purpose: Cover letter for anv_cem

\magnification=\magstep1
\input /home/zender/tex/lettermacros %contains acutal letter formatting rules

\addressdefine
\formalletterhead

\address
Abby A. Hodges, Editorial Assistant
Journal of the Atmospheric Sciences
Atmospheric Science Department
Colorado State University
Fort Collins, CO 80523-1371

\body
Dear Ms. Hodges,

In response to the request of a reviewer of JAS MS 54WC21, ``A
prognostic ice cloud parameterization for {GCM}s based on modeled and
observed behavior of tropical anvils'', the following items are
enclosed: 

\item{1.} A copy of Grabowski, W.W., M.W. Moncrieff, and J.T. Kiehl,
              1995: Long-term behavior of precipitating tropical 
                cloud systems:  A numerical study.  Submitted
                to Quart. J. Roy. Meteor. Soc.

\item{2.} Unfortunately, the CCM3 technical note (Kiehl, J.T., et al.,
                1996: Description of NCAR Community Climate Model
                (CCM3).  NCAR Tech. Note.  In preparation.) is not in
                print yet, so is not available to the reviewer. 
Instead, we have enclosed a two page excerpt (from another Zender and
Kiehl manuscript) which describes the diagnostic treatment of
condensate employed in CCM3.  

Finally, we have discovered a small error in the manuscript which we
wish to bring to the attention of the reviewer:  
there should be no factor of $\rho$ in the denominator of the
$c_4$ term in equations 2 and~3.
The CCM3 technical note is cited as the source for the empirical
parameter $c_4$---in fact $c_4$ is identical to the parameter $k_E$
used in Hilding Sundqvist, Erik Berge, and Jon Egill Kristjansson,
1989 ``Condensation and Cloud Parameterization Studies with a
Mesoscale Numerical Weather Prediction Model'', Monthly Weather
Review, 117, p. 1644. 
We use the value in their Table~1. 
Accordingly, the value of $c_4$ in our Table~1 should read $1 \times
10^{-5}$~m~kg$^{-1/2}$~s$^{-1/2}$ (as in Sundqvist et al., 1989) not
$1 \times 10^{-5}$~m$^{-2}$~kg$^{1/2}$~s$^{-1/2}$.  
This error does not affect the rest of the paper.

We think the enclosed information will satisfy the reviewer's request. 
Thank you for your editorial assistance.

%The CCM3 technical note makes clear functional form for the
%evaporation of precipitation is a modified form of Sundqvist's method
%The modification is that the cloud fraction dependence has been omitted. 

% The line after \closing goes before signature, others come after.
\closing 
Sincerely,
Charles S. Zender

\annotations % cc'ing and/or typist's initials go after this
Enclosures
%cc: J.T. Kiehl

%\ps % any postscripts go after this
%P. S. \ 

\endletter % close up the letter
%\makelabel % print out a mailing label for the envelope?
\bye % close up the TeX-shop

